---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```


# Introduction

The `vvcanvas` package is designed to interact with the Canvas Learning Management System (LMS) API. This vignette provides a basic guide on how to authenticate, retrieve course information, and fetch specific details using the package.

# Installation

To install the `vvcanvas` package, you can use the following command:

```{r setup}
install_github("vusaverse/vvcanvas")
library(vvcanvas)
```


# Authentication

To start using the package, you need to authenticate with the Canvas LMS API using your API key and base URL. Here's an example of how to authenticate:

```{r authenticate}
# Replace the placeholders with your API key and base URL
api_key <- "YOUR_API_KEY"
base_url <- "https://your_canvas_domain.com"

# Authenticate with the Canvas LMS API
canvas <- canvas_authenticate(api_key, base_url)

```


# Retrieving Course Information

Once authenticated, you can retrieve course information using the get_courses function. Here's an example:

```{r retrieve}
# Fetch the dataframe of courses
courses <- get_courses(canvas)

head(courses)

```

# Fetching Specific Details

The `vvcanvas` package provides various functions to fetch specific details. For example, to retrieve the assignments within a course, you can use the get_assignments function:


```{r assignments}
# Replace the placeholder with the desired course ID
course_id <- 12345

# Fetch the assignments for the course
assignments <- get_assignments(canvas, course_id)
head(assignments)

```

