---
title: "Uploading QTI Files and Updating Quiz Parameters in Canvas LMS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Uploading QTI Files and Updating Quiz Parameters in Canvas LMS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(vvcanvas)
```


## Introduction

This vignette demonstrates how to upload a QTI file to Canvas LMS, retrieve the list of quizzes before and after the upload, and update quiz parameters using R. The process involves using the `get_course_quizzes` and `update_quiz` functions.

## Step 1: Authenticate with Canvas

First, authenticate with Canvas by creating a canvas object containing your API key and base URL:

```{r}  
canvas <- vvcanvas::canvas_authenticate()

```

## Step 2: Retrieve the List of Quizzes

Retrieve the list of quizzes in a course before uploading the QTI file: 


```{r}
course_id <- "12345"  # Replace with your actual course ID
quizzes_before <- get_course_quizzes(canvas, course_id)

```


## Step 3: Upload the QTI File

Use the `upload_qti_file_with_migration` function to upload your QTI file. This function should be defined to handle the QTI file upload process: 
 

```{r}
# Define the function if not already defined


# Upload the QTI file
file_path <- "path/to/your/qti_file.zip"  # Replace with your actual file path
upload_qti_file_with_migration(canvas, course_id = course_id, file_path = "qti_file.zip", pre_attachment_size = "12345", pre_attachment_name = "test")

```

## Step 4: Retrieve Quizzes After Upload
Retrieve the list of quizzes again after the QTI file upload: 
 
```{r}
quizzes_after <- get_course_quizzes(canvas, course_id)
print(quizzes_after)
```

## Step 5: Identify the New Quiz

Compare the lists of quizzes before and after the upload to identify the newly created quiz: 

```{r}

new_quiz <- setdiff(quizzes_after, quizzes_before)
print(new_quiz)

```

## Step 6: Update Quiz Parameters

Use the update_quiz function to modify the parameters of the newly created quiz: 

```{r}

quiz_id <- new_quiz$id  # Assuming there's only one new quiz
quiz_params <- list(
  title = "Updated Quiz Title",
  description = "Updated description of the quiz.",
  due_at = "2013-01-23T23:59:00-07:00"
)

updated_quiz <- update_quiz(canvas, course_id, quiz_id, quiz_params)
print(updated_quiz)

```

## Conclusion
This vignette demonstrated how to upload a QTI file to Canvas LMS, identify the newly created quiz, and update its parameters. You can extend this process to modify other quiz attributes as needed.
